**Load packages**
```{r}
options(repos = c(CRAN = "https://cloud.r-project.org"))
library(dplyr)
library(tidyr)
library(stringr)
install.packages("googlesheets4")
library(googlesheets4)
library(nnet)
library(ggplot2)

```
**Prepare for GPA**
```{r}
library(readxl)


file_path <- "/Users/fuyitong/Library/Containers/com.microsoft.Outlook/Data/tmp/Outlook Temp/umbc_grades[4].xlsx"


dfgpa <- read_excel(file_path)

```

```{r}
library(dplyr)

#letter grades to quality points (from University web)
dfgpa <- dfgpa %>%
  mutate(QualityPoints = case_when(
    Grade == "A" ~ 4,
    Grade == "B" ~ 3,
    Grade == "C" ~ 2,
    Grade == "D" ~ 1,
    Grade == "F" ~ 0,
    TRUE ~ NA_real_
  ))

dfgpa$EmployeeID <- as.character(dfgpa$EmployeeID)

#first 3 unique terms per student
df_first3terms <- dfgpa %>%
  group_by(EmployeeID) %>%
  mutate(term_rank = dense_rank(Term)) %>%
  filter(term_rank <= 3) %>%
  ungroup()

#filter NA (Pass Fail Grades)
df_gpa_terms_3 <- df_first3terms %>%
  filter(!is.na(QualityPoints))


#calculate cumulative GPA 3 semesters
student_gpa_3 <- df_gpa_terms_3 %>%
  group_by(EmployeeID) %>%
  summarise(
    total_quality_points_3term = sum(QualityPoints * CreditsAttempted, na.rm = TRUE),
    total_credits_3term = sum(CreditsAttempted, na.rm = TRUE),
    avg_gpa_3term = total_quality_points_3term / total_credits_3term
  ) %>%
  ungroup()

#first 2 unique terms per student
df_first2terms <- dfgpa %>%
  group_by(EmployeeID) %>%
  mutate(term_rank = dense_rank(Term)) %>%
  filter(term_rank <= 1) %>% ##1 represents the first 2 semesters, 1 represent the first semester
  ungroup()

df_gpa_terms_2 <- df_first2terms %>%
  filter(!is.na(QualityPoints))

#calculate cumulative GPA 2 semesters
student_gpa_2 <- df_gpa_terms_2 %>%
  group_by(EmployeeID) %>%
  summarise(
    total_quality_points_2term = sum(QualityPoints * CreditsAttempted, na.rm = TRUE),
    total_credits_2term = sum(CreditsAttempted, na.rm = TRUE),
    gpa_2term = total_quality_points_2term / total_credits_2term
  ) %>%
  ungroup()

#combine
student_gpa <- student_gpa_3 %>%
  left_join(student_gpa_2, by = "EmployeeID")

student_gpa

#check NAs
sum(is.na(student_gpa))

```
```{r}
install.packages("writexl")
library(writexl)

write_xlsx(student_gpa, path = "/Users/fuyitong/Documents/PULSE Summer Project/student_gpa_first3terms.xlsx")

```

```{r}
dflist <- read.csv("/Users/fuyitong/Library/Containers/com.microsoft.Outlook/Data/tmp/Outlook Temp/idlist.csv")  
```

**Read csv**

```{r}
df <- read.csv("https://uwmadison.box.com/shared/static/fbt91lylf2ue0kmlylug2c56sceebjk8.csv")

head(df)

```

**Merge GPA into the main df**
```{r}
dflist <- dflist %>%
  mutate(
    StudentID = as.character(StudentID),
    EmployeeID = as.character(EmployeeID)
  )

student_gpa <- student_gpa %>%
  mutate(EmployeeID = as.character(EmployeeID))

df <- df %>%
  mutate(StudentID = as.character(StudentID))


dflist <- dflist %>%
  left_join(student_gpa, by = "EmployeeID")


df <- df %>%
  left_join(dflist, by = "StudentID")


head(df)

sum(is.na(df$avg_gpa_3term))
sum(is.na(df$gpa_2term))
na_rows <- df[is.na(df$avg_gpa_3term), ]
na_rows[, c("StudentID", "EmployeeID", "total_quality_points_3term", "total_credits_3term")]
df <- df[!is.na(df$avg_gpa_3term), ]
```

**Code and check independent variables**
```{r}
df$Female <- ifelse(df$Female == "Female", 1, 0)   
df$URM    <- ifelse(df$URM == "URM", 1, 0)  
df$FG     <- ifelse(df$FG == "FG", 1, 0)

table(df$FG)
table(df$URM)
table(df$Female)
table(df$URM, df$Female)

sum(is.na(df$Female))
sum(is.na(df$URM))
sum(is.na(df$FG))
#since there is an NA both in FG and Female, drop these two data
df <- df %>%
  filter(!is.na(Female) & !is.na(FG))

```

**Find original and final major**
```{r}
semester_order <- c(
  "fa17", "wi18", "sp18", "su18", 
  "fa18", "wi19", "sp19", "su19",
  "fa19", "wi20", "sp20", "su20", 
  "fa20", "wi21", "sp21", "su21", 
  "fa21", "wi22", "sp22", "su22", 
  "fa22", "wi23", "sp23", "su23", 
  "fa23", "wi24", "sp24", "su24", 
  "fa24"
)
plan_cols <- grep("^plan_", names(df), value = TRUE)

term_labels <- sub("^plan_", "", plan_cols)
ordered_plan_cols <- plan_cols[order(match(term_labels, semester_order))]

df$original_major <- NA
df$final_major <- NA

for (i in 1:nrow(df)) {
  df$Semester <- tolower(gsub("^F", "fa", df$Semester))
  enter_sem <- df$Semester[i]
  original_col <- paste0("plan_", enter_sem)
  completion_sem <- df$completion_term[i]
  final_col <- paste0("plan_", completion_sem)
  
  plan_values <- df[i, ordered_plan_cols]
  non_na <- plan_values[!is.na(plan_values)]
  
  if (original_col %in% names(df)) {
    major <- df[i, original_col]
    if (!is.na(major)) {
      df$original_major[i] <- major
    } else if (length(non_na) > 0) {
      df$original_major[i] <- head(non_na, 1)
    }
  } else if (length(non_na) > 0) {
    df$original_major[i] <- head(non_na, 1)
  }
  
  if (final_col %in% names(df)) {
    major_final <- df[i, final_col]
    if (!is.na(major_final)) {
      df$final_major[i] <- major_final
    } else if (length(non_na) > 0) {
      df$final_major[i] <- tail(non_na, 1)
    }
  } else if (length(non_na) > 0) {
    df$final_major[i] <- tail(non_na, 1)
  }
}

df[is.na(df$original_major), ]
df[is.na(df$final_major), ] #these two are dropped when dropping uncodable original&final major STEM requirements

```


```{r}
head(df[, c("StudentID", "URM", "Female", "Semester", "original_major", "final_major")])

```

**Read stem requirement google sheet**

```{r}
sheet_url <- "https://docs.google.com/spreadsheets/d/1uddE0gpDYKFG2TNGv6QyUkmu9nyHybNmg0Qfz5mu_CI/edit?usp=sharing"

sheet_names(sheet_url)
gs4_auth()
stem_req <- read_sheet(sheet_url, sheet = "Coding")


```

**Code original and final major stem requirement**

```{r}
df$original_stem_req <- NA
df$final_stem_req <- NA

for (i in 1:nrow(df)) {
  major1 <- df$original_major[i]
  major2 <- df$final_major[i]

  #original major STEM req
  if (!is.na(major1)) {
    row_index <- which(stem_req$Plan == major1)
    if (length(row_index) > 0) {
      df$original_stem_req[i] <- stem_req[[ "STEM credits requirements" ]][row_index[1]]
    }
  }

  #final major STEM req
  if (!is.na(major2)) {
    row_index <- which(stem_req$Plan == major2)
    if (length(row_index) > 0) {
      df$final_stem_req[i] <- stem_req[[ "STEM credits requirements" ]][row_index[1]]
    }
  }
}

df$stem_req_change <- df$final_stem_req - df$original_stem_req


```




**Standardize/clean majors to take care of the pre tracks**
```{r}
standardize_major <- function(major) {
  major <- tolower(major)
  major <- gsub("^pre-+", "", major)
  major <- trimws(major)
  
  #add "- bs" for pre majors to match their counterparts
  bs_majors <- c(
    "mechanical engineering",
    "chemical engineering",
    "computer engineering",
    "computer science"
  )
  
  major <- ifelse(major %in% bs_majors, paste0(major, " - bs"), major)
  
  return(major)
}

#apply to both datasets
df$original_major_clean <- standardize_major(df$original_major)
df$final_major_clean <- standardize_major(df$final_major)
stem_req$Plan_clean <- standardize_major(stem_req$Plan)

```

**Check NAs**

```{r}
df$stem_req_change <- df$final_stem_req - df$original_stem_req
df_na <- df[is.na(df$stem_req_change), c("original_major", "final_major")]
df_na

df <- df[!is.na(df$stem_req_change), ]

```



**Code whether or not a student switched major**
```{r}
df$switched_major <- ifelse(
  df$original_major_clean != df$final_major_clean, 
  1, 0
)

print(df[1:20, c("original_major_clean", "final_major_clean", "switched_major")])


```

**Code whether or not a student switched from a stem to nonstem major**
```{r}
df$original_stem <- NA
df$final_stem <- NA

for (i in 1:nrow(df)) {
  major1 <- df$original_major_clean[i]
  major2 <- df$final_major_clean[i]
  
  match1 <- stem_req$stem[stem_req$Plan_clean == major1][1]
  match2 <- stem_req$stem[stem_req$Plan_clean == major2][1]
  
  df$original_stem[i] <- match1
  df$final_stem[i] <- match2
}

df$stem_to_nonstem <- ifelse(
  !is.na(df$original_stem) &
  !is.na(df$final_stem) &
  df$original_stem == "yes" &
  df$final_stem == "no",
  1,  
  0
)
  
df$nonstem_to_stem <- ifelse(
  !is.na(df$original_stem) &
  !is.na(df$final_stem) &
  df$original_stem == "no" &
  df$final_stem == "yes",
  1,  
  0   
)

df$stem_to_stem <- ifelse(
  !is.na(df$original_stem) &
  !is.na(df$final_stem) &
  df$original_stem == "yes" &
  df$final_stem == "yes",
  1,  
  0  
)

df$nonstem_to_nonstem <- ifelse(
  !is.na(df$original_stem) &
  !is.na(df$final_stem) &
  df$original_stem == "no" &
  df$final_stem == "no",
  1,  
  0   
)

sum(df$stem_to_nonstem == 1, na.rm = TRUE)
sum(df$nonstem_to_stem == 1, na.rm = TRUE)
sum(df$stem_to_stem == 1, na.rm = TRUE)
sum(df$nonstem_to_nonstem == 1, na.rm = TRUE)


df_stem_students <- df[df$original_stem == "yes",]
df_stem_students$stem_to_nonstem <- ifelse(
  !is.na(df_stem_students$original_stem) &
  !is.na(df_stem_students$final_stem) &
  df_stem_students$original_stem == "yes" &
  df_stem_students$final_stem == "no",
  1,  
  0
)

```

**Code students' changing department/school status**
```{r}
df$original_dept <- NA
df$final_dept <- NA
df$original_college <- NA
df$final_college <- NA

for (i in 1:nrow(df)) {
  major1 <- df$original_major_clean[i]
  major2 <- df$final_major_clean[i]
  
  match1 <- stem_req[stem_req$Plan_clean == major1, ]
  if (nrow(match1) > 0) {
    df$original_dept[i] <- match1$Department[1]
    df$original_college[i] <- match1$College[1]
  }
  
  match2 <- stem_req[stem_req$Plan_clean == major2, ]
  if (nrow(match2) > 0) {
    df$final_dept[i] <- match2$Department[1]
    df$final_college[i] <- match2$College[1]
  }
}

#change type
df$change_type <- NA

for (i in 1:nrow(df)) {
  if (is.na(df$original_dept[i]) | is.na(df$final_dept[i])) {
    df$change_type[i] <- NA
  } else if (df$original_major_clean[i] == df$final_major_clean[i]) {
    df$change_type[i] <- "No Change"
  } else if (df$original_dept[i] == df$final_dept[i]) {
    df$change_type[i] <- "Same Department"
  } else if (!is.na(df$original_college[i]) & !is.na(df$final_college[i]) &
             df$original_college[i] == df$final_college[i]) {
    df$change_type[i] <- "Different Department (Same College)"
  } else if (!is.na(df$original_college[i]) & !is.na(df$final_college[i])) {
    df$change_type[i] <- "Different College"
  } else {
    df$change_type[i] <- NA
  }
}

```


**Convert change_type to scores**
```{r}
df$change_score <- NA

df$change_score[df$change_type == "No Change"] <- 0
df$change_score[df$change_type == "Same Department"] <- 1
df$change_score[df$change_type == "Different Department (Same College)"] <- 2
df$change_score[df$change_type == "Different College"] <- 3

#inspect students with different change score
df[df$change_score == 1,c("original_major_clean", "final_major_clean")]
df[df$change_score == 2,c("original_major_clean", "final_major_clean")]
df[df$change_score == 3,c("original_major_clean", "final_major_clean")]

```

**Inspect dependent variables**

```{r}
n_total <- nrow(df)

outcome_summary <- data.frame(
  Variable = c("switched_major", "stem_req_change", "change_score", "stem_to_nonstem"),
  Mean = c(
    mean(df$switched_major, na.rm = TRUE),
    mean(df$stem_req_change, na.rm = TRUE),
    mean(df$change_score, na.rm = TRUE),
    mean(df$stem_to_nonstem, na.rm = TRUE)
  ),
  SD = c(
    sd(df$switched_major, na.rm = TRUE),
    sd(df$stem_req_change, na.rm = TRUE),
    sd(df$change_score, na.rm = TRUE),
    sd(df$stem_to_nonstem, na.rm = TRUE)
  ),
  Min = c(
    min(df$switched_major, na.rm = TRUE),
    min(df$stem_req_change, na.rm = TRUE),
    min(df$change_score, na.rm = TRUE),
    min(df$stem_to_nonstem, na.rm = TRUE)
  ),
  Max = c(
    max(df$switched_major, na.rm = TRUE),
    max(df$stem_req_change, na.rm = TRUE),
    max(df$change_score, na.rm = TRUE),
    max(df$stem_to_nonstem, na.rm = TRUE)
  ),
  N_Observed = c(
    sum(!is.na(df$switched_major)),
    sum(!is.na(df$stem_req_change)),
    sum(!is.na(df$change_score)),
    sum(!is.na(df$stem_to_nonstem))
  ),
  N_Missing = c(
    sum(is.na(df$switched_major)),
    sum(is.na(df$stem_req_change)),
    sum(is.na(df$change_score)),
    sum(is.na(df$stem_to_nonstem))
  )
)

outcome_summary$Missing_Pct <- round(100 * outcome_summary$N_Missing / n_total, 1)

outcome_summary


table(df$switched_major)
table(df$stem_to_nonstem)

```


```{r}
library(ggplot2)

#stem_req_change outcome check
ggplot(df, aes(x = stem_req_change)) +
  geom_histogram(bins = 30, fill = "#69b3a2", color = "white") +
  labs(title = "Distribution of stem_req_change",
       x = "stem_req_change", y = "Count") +
  theme_minimal()

#change_score
ggplot(df, aes(x = change_score)) +
  geom_histogram(bins = 30, fill = "#404080", color = "white") +
  labs(title = "Distribution of change_score",
       x = "change_score", y = "Count") +
  theme_minimal()


```

```{r}
#switched_major
ggplot(df, aes(x = factor(switched_major))) +
  geom_bar(fill = "#F8766D") +
  labs(title = "Distribution of switched_major",
       x = "switched_major (0/1)", y = "Count") +
  theme_minimal()

#stem_to_nonstem
ggplot(df, aes(x = factor(stem_to_nonstem))) +
  geom_bar(fill = "#00BFC4") +
  labs(title = "Distribution of stem_to_nonstem",
       x = "stem_to_nonstem (0/1)", y = "Count") +
  theme_minimal()

```


**Predicting whether or not a student switched major**

```{r}

#main effects
model1_main <- glm(switched_major ~ Female + URM + avg_gpa_3term + FG, 
                   data = df, family = "binomial")
summary(model1_main)
roubustness1_main <- glm(switched_major ~ Female + URM + gpa_2term + FG, 
                   data = df, family = "binomial")
summary(roubustness1_main)

#added interaction
model1 <- glm(switched_major ~  Female * URM + Female * FG + URM * FG + avg_gpa_3term, data = df, family = "binomial")
summary(model1)

roubustness1 <- glm(switched_major ~  Female * URM + Female * FG + URM * FG + gpa_2term, data = df, family = "binomial")
summary(roubustness1)
```

```{r}
#main effects
model2_main <- lm(stem_req_change ~ Female + URM + FG + avg_gpa_3term, data = df)
summary(model2_main)

roubustness2_main <- lm(stem_req_change ~ Female + URM + FG + gpa_2term, data = df)
summary(roubustness2_main)

#added interaction effects
model2 <- lm((stem_req_change) ~  Female * URM + Female * FG + URM * FG + avg_gpa_3term, data = df)
summary(model2)

roubustness2 <- lm((stem_req_change) ~  Female * URM + Female * FG + URM * FG + gpa_2term, data = df)
summary(roubustness2)


```
```{r}
#focus on students who change their major
df_changed <- subset(df, stem_req_change != 0)
model2_changed <- lm(stem_req_change ~ Female * URM + Female * FG + URM * FG + avg_gpa_3term, data = df_changed)
summary(model2_changed)

```


```{r}
#main effects
model3_main <- lm(change_score ~ Female + URM + FG + avg_gpa_3term, data = df)
summary(model3_main)

roubustness3_main <- lm(change_score ~ Female + URM + FG + gpa_2term, data = df)
summary(roubustness3_main)

#interaction added
model3 <- lm(change_score ~ Female * URM + Female * FG + URM * FG + avg_gpa_3term, data = df)
summary(model3)

robustness3 <- lm(change_score ~ Female * URM + Female * FG + URM * FG + gpa_2term, data = df)
summary(robustness3)

#focus on students who changed their major
df_nonzero <- subset(df, change_score != 0)
model3_main <- lm(change_score ~ Female * URM + Female * FG + URM * FG + avg_gpa_3term, data = df_nonzero)
summary(model3_main)

```

```{r}
#main effects
model4_main <- glm(stem_to_nonstem ~ Female + URM + FG + avg_gpa_3term, family = "binomial", data = df)
summary(model4_main)

robustness4_main <- glm(stem_to_nonstem ~ Female + URM + FG + gpa_2term, family = "binomial", data = df)
summary(robustness4_main)

#interaction added
model4 <- glm(formula = stem_to_nonstem ~ Female * URM + FG * URM + FG * Female + avg_gpa_3term, family = "binomial", data = df)

summary(model4)

robustness4 <- glm(formula = stem_to_nonstem ~ Female * URM + FG * URM + FG * Female + gpa_2term, family = "binomial", data = df)

summary(robustness4)

#focus on stem students
model4_stemstudents <- glm(formula = stem_to_nonstem ~ Female * URM + FG * URM + FG * Female + avg_gpa_3term, family = "binomial", data = df_stem_students)
summary(model4_stemstudents)
```
```{r}
#predict using model
df$predicted <- predict(model2, newdata = df)

#recode feamle and URM
df$Female_label <- ifelse(df$Female == 1, "Female",
                     ifelse(df$Female == 0, "Male", NA))
df$URM_label    <- ifelse(df$URM == 1, "URM",
                     ifelse(df$URM == 0, "Not URM", NA))



df_summary_pred <- df %>%
  group_by(Female_label, URM_label) %>%
  summarise(
    predicted_mean = mean(abs(predicted), na.rm = TRUE),
    n = n(),
    .groups = "drop"
  )


ggplot(df_summary_pred, aes(x = Female_label, y = predicted_mean, fill = URM_label)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    title = "Model-Predicted Interaction: Female × URM",
    x = "Sex",
    y = "Change in STEM Credits (abs value)",
    fill = "URM Status"
  ) +
  theme_minimal()


male_urm_pred <- df_summary_pred %>%
  filter(Female_label == "Male", URM_label == "URM") %>%
  pull(predicted_mean)

female_urm_pred <- df_summary_pred %>%
  filter(Female_label == "Female", URM_label == "URM") %>%
  pull(predicted_mean)

difference <- male_urm_pred - female_urm_pred
difference

```
**read csv**
```{r}
library(readr)
survey <- read_csv("/Users/fuyitong/Documents/PULSE Summer Project/umbc_survey_data.csv")
```
**merge demographic info**
```{r}
# merge demographic info (FG, Female, URM) from df into survey by StudentID
survey <- survey %>%
  left_join(df %>% select(StudentID, FG, Female, URM), by = "StudentID")


```

**filter the data that are not available in df**
```{r}

survey <- survey %>%
  filter(!is.na(FG) & !is.na(Female) & !is.na(URM))

```
**check the number of URM female students**
```{r}

table(survey$URM, survey$Female)
```
**drop NAs**
```{r}
#the results show that for the first 15 plan_models 5 data are missing - check these data and filter out
missing_rows <- survey %>%
  filter(is.na(why_plans_1) | is.na(Female) | is.na(URM) | is.na(FG))

nrow(missing_rows)


missing_rows[, c("FG", "URM", "why_plans_1")]


survey_filtered <- survey %>%
  filter(!is.na(why_plans_2) & !is.na(Female) & !is.na(URM) & !is.na(FG))
```

**drop NAs**
```{r}
#the results show that 83 data are still missing for plan_model 16, 17, and 18, so check these data and drop them for the three models
missing_rows <- survey %>%
  filter(is.na(why_plans_18) | is.na(Female) | is.na(URM) | is.na(FG))

nrow(missing_rows)


missing_rows


survey_filtered_2 <- survey %>%
  filter(!is.na(why_plans_16) & !is.na(Female) & !is.na(URM) & !is.na(FG))
```
**build main effect models**
```{r}

model_plan_1 <- lm(why_plans_1 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_1)

model_plan_2 <- lm(why_plans_2 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_2)

model_plan_3 <- lm(why_plans_3 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_3)

model_plan_4 <- lm(why_plans_4 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_4)

model_plan_5 <- lm(why_plans_5 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_5)

model_plan_6 <- lm(why_plans_6 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_6)

model_plan_7 <- lm(why_plans_7 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_7)

model_plan_8 <- lm(why_plans_8 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_8)

model_plan_9 <- lm(why_plans_9 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_9)

model_plan_10 <- lm(why_plans_10 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_10)

model_plan_11 <- lm(why_plans_11 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_11)

model_plan_12 <- lm(why_plans_12 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_12)

model_plan_13 <- lm(why_plans_13 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_13)

model_plan_14 <- lm(why_plans_14 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_14)

model_plan_15 <- lm(why_plans_15 ~ Female + URM + FG, data = survey_filtered)
summary(model_plan_15)

model_plan_16 <- lm(why_plans_16 ~ Female + URM + FG, data = survey_filtered_2)
summary(model_plan_16)

model_plan_17 <- lm(why_plans_17 ~ Female + URM + FG, data = survey_filtered_2)
summary(model_plan_17)

model_plan_18 <- lm(why_plans_18 ~ Female + URM + FG, data = survey_filtered_2)
summary(model_plan_18)

```

**build modles with interaction terms**
```{r}
model1 <- lm(why_plans_1 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model1)

model2 <- lm(why_plans_2 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model2)

model3 <- lm(why_plans_3 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model3)

model4 <- lm(why_plans_4 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model4)

model5 <- lm(why_plans_5 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model5)

model6 <- lm(why_plans_6 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model6)

model7 <- lm(why_plans_7 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model7)

model8 <- lm(why_plans_8 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model8)

model9 <- lm(why_plans_9 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model9)

model10 <- lm(why_plans_10 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model10)

model11 <- lm(why_plans_11 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model11)

model12 <- lm(why_plans_12 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model12)

model13 <- lm(why_plans_13 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model13)

model14 <- lm(why_plans_14 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model14)

model15 <- lm(why_plans_15 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered)
summary(model15)

model16 <- lm(why_plans_16 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered_2)
summary(model16)

model17 <- lm(why_plans_17 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered_2)
summary(model17)

model18 <- lm(why_plans_18 ~ Female + URM + FG + Female * URM + Female * FG + URM * FG, data = survey_filtered_2)
summary(model18)
```

```{r}

new_data <- expand.grid(
  Female = c(0, 1),
  URM = c(0, 1),
  FG = mean(survey_filtered$FG, na.rm = TRUE)  # hold FG constant
)

new_data$predicted <- predict(model6, newdata = new_data)

new_data <- new_data %>%
  mutate(
    Female_label = ifelse(Female == 1, "Female", "Male"),
    URM_label = ifelse(URM == 1, "URM", "Non-URM")
  )

ggplot(new_data, aes(x = URM_label, y = predicted, fill = Female_label)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    title = "Interaction Effect of Female and URM on why_plans_6 (help other people)",
    x = "URM Status",
    y = "Predicted why_plans_6",
    fill = "Gender"
  ) +
  theme_minimal()
```
```{r}
new_data9 <- expand.grid(
  Female = c(0, 1),
  URM = c(0, 1),
  FG = mean(survey_filtered$FG, na.rm = TRUE)  # hold FG constant
)

new_data9$predicted <- predict(model9, newdata = new_data9)


new_data9 <- new_data9 %>%
  mutate(
    Female_label = ifelse(Female == 1, "Female", "Male"),
    URM_label = ifelse(URM == 1, "URM", "Non-URM")
  )


ggplot(new_data9, aes(x = URM_label, y = predicted, fill = Female_label)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    title = "Interaction Effect of Female and URM on why_plans_9 (make contribution to society)",
    x = "URM Status",
    y = "Predicted Value",
    fill = "Gender"
  ) +
  theme_minimal()
```

